ReactionBarrierAnalysis

### 2024-11-30 Code/ReactionBarrierAnalysis.Rmd
Added dq supplemental analysis

>>>>

### Disqualification Analysis
An earlier form of this paper did not originally include times from athlete's
who were disqualified, but response from reviewer's prompted us to question
whether we could include these times.  While we ultimately chose to include
positive reaction times from athlete's who were disqualified, this section of
the supplement is dedicated to investigating how much these times matter and
examining the effect of a few but important times on the overall model.  These
times are important because most of them fall on the left tail of the
distribution, which is the part that we care the most about predicting accurately.

```{r}
dhm_nodq <- times |>
  filter(Type == "F" | Type == "S") |>
  filter(Gender == "M") |>
  filter(Time != "DNS", Time != "DQ", Time != "D") |>
  filter(RxnTime > 0) |>
  filter(Event == "100 Dash" | Event == "110 Hurdles")

nrow(dhm) - nrow(dhm_nodq)
```
We see that there are 17 male athletes that had positive reaction times but were
disqualified.  Not all of these athletes were disqualified for having reaction
times less than 0.1 seconds, in many instances these athletes could have been
disqualified for failed drug tests and other infractions.

Now we fit the model.
```{r}
gg3b_nodq <- gamlss(RxnTime ~ random(Venue), sigma.formula = ~ random(Heat),
                    data = dhm_no2022, family = GG, control = gamlss.control(n.cyc = 40))
```

Let us see how we did with residuals
```{r}
qq_conf_plot(resid(gg3b_nodq))
```
The standardized residual plot looks quite strong.  We are now ready to simulate
to examine how extreme certain reaction times are.

```{r}
samplefit_nodq <- simfit(gg3b_nodq)
```

The results below appear in table 4 of the supplement

```{r}
mean(samplefit_nodq < .10)
mean(samplefit_nodq < .09)
mean(samplefit_nodq < .08)
```
We see that these times are smaller when remove disqualifications than when we
leave them in.  This is not surprising, as we know that some disqualifications
come from values between 0 and 0.1.  Thus including those values is going to
alter the model and raise the probability of athletes reacting in the 0 to 0.1
range.
